---
title: "Autistic brain dynamics and responsivity to multi-target pharmaco-challenge with Cannabidivarin (CBDV)"
output: html_document
date: "2026-04-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(openxlsx)
library(tidyverse)
```

# core network strength
```{r}
core_network_strength_cbd <- read.xlsx("core_network_strength_0909.xlsx")
core_network_strength_cbd$asd <- as.factor(core_network_strength_cbd$asd)
core_network_strength_cbd$drug<- as.factor(core_network_strength_cbd$drug)
core_network_strength_cbd <- core_network_strength_cbd %>% 
  separate(id_sess, into = c("id", "order"), sep = -1, remove = FALSE)
core_network_strength_cbd$order<- as.factor(core_network_strength_cbd$order)
core_network_strength_cbd$id <- as.character(core_network_strength_cbd$id)
```

```{r}
core_network_strength_cbd_plb <- core_network_strength_cbd %>% 
  filter(drug == "0")
core_network_strength_cbd_cbdv <- core_network_strength_cbd %>% 
  filter(drug != "1")
core_network_strength_cbd_cbdv_only <- core_network_strength_cbd %>% 
  filter(drug == "2")
core_network_strength_cbd_cbdv_ny <- core_network_strength_cbd_cbdv%>% 
  filter(asd == "0")
core_network_strength_cbd_cbdv_asd <- core_network_strength_cbd_cbdv %>% 
  filter(asd == "1")
```

# motion
```{r}
summary(lm(data = core_network_strength_cbd_cbdv, meanFD_246 ~ asd * drug))

t.test(core_network_strength_cbd_plb$meanFD_246 ~ core_network_strength_cbd_plb$asd)
t.test(core_network_strength_cbd_cbdv_only$meanFD_246 ~ core_network_strength_cbd_cbdv_only$asd)
t.test(core_network_strength_cbd_cbdv_ny$meanFD_246 ~ core_network_strength_cbd_cbdv_ny$drug)
t.test(core_network_strength_cbd_cbdv_asd$meanFD_246 ~ core_network_strength_cbd_cbdv_asd$drug)

core_network_strength_cbd_cbdv%>% 
  group_by(asd, drug) %>% 
  ggpubr::get_summary_stats(meanFD_246, type = "mean_sd")
```

### IC 0
```{r}
summary(lm(scale(ic000) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) , data = core_network_strength_cbd_plb)) # asd1        -0.0139929  0.0123315  -1.135   0.2668 
summary(lm(scale(ic000) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) + order , data = core_network_strength_cbd_plb))
summary(lmerTest::lmer(scale(ic000) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + (1|id), data = core_network_strength_cbd_cbdv))
# drug2             -0.29721    0.24432 25.73294  -1.216   0.2348
# asd1:drug2         0.13324    0.50941 27.24108   0.262   0.7956 
summary(lmerTest::lmer(scale(ic000) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + order + (1|id), data = core_network_strength_cbd_cbdv))
# drug2             -0.33233    0.25554 26.13178  -1.301   0.2048 
# asd1:drug2         0.02296    0.54380 26.89918   0.042   0.9666 
```
### IC 1
```{r}
summary(lm(scale(ic001) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) , data = core_network_strength_cbd_plb)) 
# asd1              -0.25458    0.42049  -0.605  0.55015  
summary(lm(scale(ic001) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) + order , data = core_network_strength_cbd_plb))
# asd1              -0.48858    0.41044  -1.190  0.24554  
# scale(meanFD_246)  0.66934    0.22542   2.969  0.00668 **
# orderB            -0.90668    0.37976  -2.388  0.02519 *
summary(lmerTest::lmer(scale(ic001) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + (1|id), data = core_network_strength_cbd_cbdv))
# drug2             -0.01650    0.13944 21.02570  -0.118  0.90693
summary(lmerTest::lmer(scale(ic001) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + order + (1|id), data = core_network_strength_cbd_cbdv))
# drug2             -0.0695699  0.1496936 19.3874141  -0.465  0.64729
```
### IC 2
```{r}
summary(lm(scale(ic002) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) , data = core_network_strength_cbd_plb)) 
# asd1              -0.25504    0.43644  -0.584    0.564  
summary(lm(scale(ic002) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) + order , data = core_network_strength_cbd_plb))
# asd1              -0.44705    0.43038  -1.039   0.3093 

summary(lmerTest::lmer(scale(ic002) ~ asd*drug + scale(age) + scale(IQ) + scale(meanFD_246) + (1|id), data = core_network_strength_cbd_cbdv))
summary(lmerTest::lmer(scale(ic002) ~ asd*drug + scale(age) + scale(IQ) + scale(meanFD_246) + order + (1|id), data = core_network_strength_cbd_cbdv))
# asd1:drug2         0.73822    0.31074 23.61129   2.376   0.0260 *
summary(lmerTest::lmer(scale(ic002) ~ drug + scale(age) + scale(IQ) + scale(meanFD_246) + order + (1|id), data = core_network_strength_cbd_cbdv_ny))
# drug2             -0.09853    0.09513  7.42542  -1.036    0.333 
summary(lmerTest::lmer(scale(ic002) ~ drug + scale(age) + scale(IQ) + scale(meanFD_246) + order + (1|id), data = core_network_strength_cbd_cbdv_asd))
# drug2              0.62885    0.36359 11.29738   1.730    0.111

model_ic2_interaction <- lme4::lmer(scale(ic002) ~ asd*drug + scale(age) + scale(IQ) + scale(meanFD_246) + (1|id), data = core_network_strength_cbd_cbdv, REML = FALSE) # 128.88 146.44
model_ic2_order_interaction <- lme4::lmer(scale(ic002) ~ asd*drug + scale(age) + scale(IQ) + scale(meanFD_246) + order + (1|id), data = core_network_strength_cbd_cbdv) # 128.03 149.50
anova(model_ic2_interaction, model_ic2_order_interaction)
emmeans::emmeans(model_ic2_order_interaction, list(pairwise ~ drug|asd))
```
### IC 3
```{r}
summary(lm(scale(ic003) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) , data = core_network_strength_cbd_plb)) 
# asd1              -0.25504    0.43644  -0.584    0.564  
summary(lm(scale(ic003) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) + order , data = core_network_strength_cbd_plb))
# asd1              -0.44705    0.43038  -1.039   0.3093 

summary(lmerTest::lmer(scale(ic003) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + (1|id), data = core_network_strength_cbd_cbdv))
# asd1               0.87629    0.33701 28.10301   2.600   0.0147 *
# asd1:drug2          0.5404     0.4202 26.6307   1.286   0.2095
summary(lmerTest::lmer(scale(ic003) ~ asd * drug + scale(age) + scale(IQ) + scale(meanFD_246) + order + (1|id), data = core_network_strength_cbd_cbdv))
# asd1               0.83953    0.33909 27.80698   2.476   0.0197 *
# asd1:drug2         0.652643   0.447622 26.433104   1.458    0.157
```
### IC 4
```{r}
summary(lm(scale(ic004) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) , data = core_network_strength_cbd_plb)) 
# asd1               -0.3545     0.3863  -0.918   0.3673   
summary(lm(scale(ic004) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) + order , data = core_network_strength_cbd_plb))

summary(lmerTest::lmer(scale(ic004) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + (1|id), data = core_network_strength_cbd_cbdv))
# drug2             -0.003804   0.237202 24.656364  -0.016   0.9873
# asd1:drug2         0.05586    0.49828 26.37970   0.112   0.9116
summary(lmerTest::lmer(scale(ic004) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + order + (1|id), data = core_network_strength_cbd_cbdv))
# drug2              0.03818    0.24891 25.59064   0.153   0.8793 
```
### IC 6
```{r}
summary(lm(scale(ic006) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) , data = core_network_strength_cbd_plb)) 
# asd1              -0.58261    0.45698  -1.275   0.2136 
summary(lm(scale(ic006) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) + order , data = core_network_strength_cbd_plb))

summary(lmerTest::lmer(scale(ic006) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + (1|id), data = core_network_strength_cbd_cbdv))
# drug2             -0.0759888  0.2629680 24.0199627  -0.289   0.7751
# asd1:drug2         0.088734   0.545958 24.325684   0.163   0.8722
summary(lmerTest::lmer(scale(ic006) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + order + (1|id), data = core_network_strength_cbd_cbdv))
# drug2             -0.0970757  0.2799134 23.6394925  -0.347   0.7318
# asd1:drug2         0.099873   0.593088 23.732535   0.168   0.8677  
```

### IC 7
```{r}
summary(lm(scale(ic007) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) , data = core_network_strength_cbd_plb)) 
# asd1               -0.2607     0.3029  -0.861    0.397 
summary(lm(scale(ic007) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) + order , data = core_network_strength_cbd_plb))

summary(lmerTest::lmer(scale(ic007) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + (1|id), data = core_network_strength_cbd_cbdv))
# drug2              0.25726    0.13426 22.94147   1.916   0.0679 
# asd1:drug2         0.34269    0.28636 27.00128   1.197    0.242
summary(lmerTest::lmer(scale(ic007) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + order + (1|id), data = core_network_strength_cbd_cbdv))
# drug2              0.248103   0.144316 22.335167   1.719   0.0994 .
# asd1:drug2         0.326818   0.313190 25.339878   1.044    0.307 
```
### IC 8
```{r}
summary(lm(scale(ic008) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) , data = core_network_strength_cbd_plb)) 
# asd1               0.06060    0.43255   0.140   0.8897 
summary(lm(scale(ic008) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) + order , data = core_network_strength_cbd_plb))
# asd1              -0.12825    0.44720  -0.287   0.7767

summary(lmerTest::lmer(scale(ic008) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + (1|id), data = core_network_strength_cbd_cbdv))
# drug2             -0.049266   0.120402 18.914602  -0.409    0.687
# asd1:drug2         0.26727    0.27456 24.79137   0.973   0.3397
summary(lmerTest::lmer(scale(ic008) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + order + (1|id), data = core_network_strength_cbd_cbdv))
# drug2             -0.08937    0.13020 17.35624  -0.686    0.502 
# asd1:drug2         0.23168    0.29850 21.71553   0.776   0.4460 
```
### IC 9
```{r}
summary(lm(scale(ic009) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) , data = core_network_strength_cbd_plb)) 
# asd1                0.3613     0.4389   0.823    0.418 
summary(lm(scale(ic009) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) + order , data = core_network_strength_cbd_plb))
# asd1               0.37476    0.45460   0.824    0.418
summary(lmerTest::lmer(scale(ic009) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + (1|id), data = core_network_strength_cbd_cbdv))
# drug2              0.04351    0.19021 23.92346   0.229   0.8210
# asd1:drug2        -0.43095    0.40394 27.46215  -1.067    0.295
summary(lmerTest::lmer(scale(ic009) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + order + (1|id), data = core_network_strength_cbd_cbdv))
# drug2              0.059360   0.205543 22.215959   0.289   0.7754 
# asd1:drug2        -0.55835    0.44425 24.84898  -1.257    0.220

```
### IC 10
```{r}
summary(lm(scale(ic010) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) , data = core_network_strength_cbd_plb)) 
# asd1               0.12737    0.46380   0.275    0.786 
summary(lm(scale(ic010) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) + order , data = core_network_strength_cbd_plb))

summary(lmerTest::lmer(scale(ic010) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + (1|id), data = core_network_strength_cbd_cbdv))
# drug2              -0.1295     0.1913 22.9757  -0.677    0.505
# asd1:drug2         0.05534    0.41067 25.51701   0.135    0.894
summary(lmerTest::lmer(scale(ic010) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + order + (1|id), data = core_network_strength_cbd_cbdv))
# drug2             -0.10652    0.20972 21.13577  -0.508    0.617
# asd1:drug2         0.21401    0.45717 22.52041   0.468    0.644
```
### IC 11
```{r}
summary(lm(scale(ic011) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) , data = core_network_strength_cbd_plb)) 
# asd1               0.96270    0.39564   2.433   0.0221 * 
summary(lm(scale(ic011) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) + order , data = core_network_strength_cbd_plb))

summary(lmerTest::lmer(scale(ic011) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + (1|id), data = core_network_strength_cbd_cbdv))
# asd1                0.8550     0.3081 26.9907   2.775   0.0099 **
# drug2              -0.1318     0.2193 25.2617  -0.601   0.5533
# asd1:drug2        -0.334794   0.445062 25.622849  -0.752   0.4588 
summary(lmerTest::lmer(scale(ic011) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + order + (1|id), data = core_network_strength_cbd_cbdv))
# asd1:drug2         -0.2299     0.4577 25.4577  -0.502   0.6198
# asd1               0.89032    0.31549 26.44960   2.822  0.00894 **
# drug2             -0.06375    0.21719 24.98722  -0.294  0.77154 
```
### IC 12
```{r}
summary(lm(scale(ic012) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) , data = core_network_strength_cbd_plb)) 
# asd1              -0.44302    0.38143  -1.161 0.256006
summary(lm(scale(ic012) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) + order , data = core_network_strength_cbd_plb))

summary(lmerTest::lmer(scale(ic012) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + (1|id), data = core_network_strength_cbd_cbdv))
# drug2             -0.09200    0.17867 24.26693  -0.515    0.611
# asd1:drug2         0.37994    0.37274 26.18189   1.019    0.317 
summary(lmerTest::lmer(scale(ic012) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + order + (1|id), data = core_network_strength_cbd_cbdv))
# drug2             -0.07860    0.19152 23.55785  -0.410    0.685 
# asd1:drug2         0.39910    0.40802 24.85076   0.978    0.337
```
### IC 13
```{r}
summary(lm(scale(ic013) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) , data = core_network_strength_cbd_plb)) 
# asd1              -0.04114    0.41693  -0.099   0.9222
summary(lm(scale(ic013) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) + order , data = core_network_strength_cbd_plb))

summary(lmerTest::lmer(scale(ic013) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + (1|id), data = core_network_strength_cbd_cbdv))
# drug2             -0.13460    0.20402 24.12095  -0.660   0.5157
# asd1:drug2         0.134006   0.434718 26.560499   0.308   0.7603  
summary(lmerTest::lmer(scale(ic013) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + order + (1|id), data = core_network_strength_cbd_cbdv))
# drug2             -0.17634    0.20875 23.76043  -0.845   0.4067 
# asd1:drug2        -0.04228    0.45147 25.35013  -0.094    0.926 
```
### IC 16
```{r}
summary(lm(scale(ic016) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) , data = core_network_strength_cbd_plb)) 
# asd1              -0.1927073  0.3373324  -0.571 0.572723 
summary(lm(scale(ic016) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) + order , data = core_network_strength_cbd_plb))
# asd1              -0.3175929  0.3444769  -0.922 0.365727   

summary(lmerTest::lmer(scale(ic016) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + (1|id), data = core_network_strength_cbd_cbdv))
# drug2              0.05498    0.12735 17.64808   0.432 0.671189
# asd1:drug2         0.348515   0.272208 23.901895   1.280    0.213 
summary(lmerTest::lmer(scale(ic016) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + order + (1|id), data = core_network_strength_cbd_cbdv))
# drug2              0.03947    0.13813 16.63417   0.286    0.779 
# asd1:drug2         0.294008   0.300185 20.893219   0.979    0.339
```
### IC 17
```{r}
summary(lm(scale(ic017) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) , data = core_network_strength_cbd_plb)) 
# asd1               0.0328091  0.3546357   0.093  0.92700  
summary(lm(scale(ic017) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) + order , data = core_network_strength_cbd_plb))
# asd1               0.04455    0.35360   0.126  0.90080 
# orderC             0.69707    0.33217   2.099  0.04656 *

summary(lmerTest::lmer(scale(ic017) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + (1|id), data = core_network_strength_cbd_cbdv))
# drug2             -0.168968   0.168856 25.330801  -1.001 0.326454
# asd1:drug2         0.003376   0.358381 27.678956   0.009 0.992551 
summary(lmerTest::lmer(scale(ic017) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + order + (1|id), data = core_network_strength_cbd_cbdv))
# drug2             -0.090012   0.178618 26.170325  -0.504 0.618521
# asd1:drug2         0.065145   0.383321 27.503024   0.170 0.866294
```
### IC 20
```{r}
summary(lm(scale(ic020) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) , data = core_network_strength_cbd_plb)) 
# asd1               0.07694    0.33398   0.230 0.819606  
summary(lm(scale(ic020) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) + order , data = core_network_strength_cbd_plb))

summary(lmerTest::lmer(scale(ic020) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + (1|id), data = core_network_strength_cbd_cbdv))
# drug2             -0.01758    0.18101 24.36660  -0.097    0.923 
# asd1:drug2         0.093222   0.377546 25.314759   0.247    0.807  
summary(lmerTest::lmer(scale(ic020) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + order + (1|id), data = core_network_strength_cbd_cbdv))
# drug2             -0.03876    0.19268 24.72556  -0.201    0.842
# asd1:drug2         0.06590    0.41001 25.09545   0.161    0.874
```
### IC 22
```{r}
summary(lm(scale(ic022) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) , data = core_network_strength_cbd_plb)) 
# asd1               -0.3393     0.3916  -0.867   0.3940   
summary(lm(scale(ic022) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) + order , data = core_network_strength_cbd_plb))
# asd1              -0.47925    0.40613  -1.180   0.2496

summary(lmerTest::lmer(scale(ic022) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + (1|id), data = core_network_strength_cbd_cbdv))
# asd1              -0.30437    0.36585 29.67868  -0.832  0.41209
# asd1:drug2         0.006973   0.306199 26.416901   0.023  0.98200 
summary(lmerTest::lmer(scale(ic022) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + order + (1|id), data = core_network_strength_cbd_cbdv))
# drug2             -0.006736   0.151211 20.961826  -0.045  0.96489
# asd1:drug2         0.144032   0.335568 23.648407   0.429  0.67165
```
### IC 24
```{r}
summary(lm(scale(ic024) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) , data = core_network_strength_cbd_plb)) 
# asd1              -0.25416    0.38567  -0.659   0.5157   
summary(lm(scale(ic024) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) + order , data = core_network_strength_cbd_plb))
# asd1              -0.09252    0.38745  -0.239  0.81329

summary(lmerTest::lmer(scale(ic024) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + (1|id), data = core_network_strength_cbd_cbdv))
# drug2             -0.19402    0.20308 19.53442  -0.955 0.351049
# asd1:drug2         0.12501    0.42382 20.20100   0.295 0.771028
summary(lmerTest::lmer(scale(ic024) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + order + (1|id), data = core_network_strength_cbd_cbdv))
# drug2             -0.20630    0.20284 18.06210  -1.017 0.322569
# asd1:drug2        -0.14089    0.44197 17.93884  -0.319 0.753575 

```
### IC 25
```{r}
summary(lm(scale(ic025) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) , data = core_network_strength_cbd_plb)) 
# asd1              -0.37760    0.44120  -0.856   0.3999   
summary(lm(scale(ic025) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) + order , data = core_network_strength_cbd_plb))
# asd1              -0.36681    0.45866  -0.800   0.4317 

summary(lmerTest::lmer(scale(ic025) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + (1|id), data = core_network_strength_cbd_cbdv))
# drug2             -0.22247    0.17614 23.43557  -1.263   0.2190  
# asd1:drug2        -0.24123    0.37477 26.78386  -0.644   0.5253
summary(lmerTest::lmer(scale(ic025) ~ asd * drug + scale(age) + scale(IQ) + scale(meanFD_246) + order + (1|id), data = core_network_strength_cbd_cbdv))
# drug2             -0.14307    0.18991 21.77429  -0.753   0.4593 
# asd1:drug2        -0.22878    0.40504 23.13980  -0.565   0.5776  
```
### IC 28
```{r}
summary(lm(scale(ic028) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) , data = core_network_strength_cbd_plb)) 
# asd1              -0.22114    0.39787  -0.556  0.58309  
summary(lm(scale(ic028) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246) + order , data = core_network_strength_cbd_plb))
# asd1              -0.42985    0.40528  -1.061  0.29941 
summary(lmerTest::lmer(scale(ic028) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + (1|id), data = core_network_strength_cbd_cbdv))
# drug2             -0.10558    0.10632 18.95891  -0.993 0.333197 
# asd1:drug2        -0.02021    0.24943 22.84329  -0.081  0.93614 
summary(lmerTest::lmer(scale(ic028) ~ asd + drug + scale(age) + scale(IQ) + scale(meanFD_246) + order + (1|id), data = core_network_strength_cbd_cbdv))
# drug2             -0.15475    0.10444 16.83272  -1.482 0.156895 
# asd1:drug2         0.08218    0.25424 19.59471   0.323  0.74993
```
# Clustering
```{r}
setwd("/Users/yange/YANGE/Phd/DFC/CBD")
library(tidyverse)
library(openxlsx)
library(lmerTest)
library(cluster)
rsn_dyn_cbdv_0509 <- read.xlsx("rsn_dyn_cbdv_0509.xlsx")
core_network_strength_cbd <- read.xlsx("core_network_strength_cbd.xlsx")
```
## Clustering PLB & CBDV
```{r}
pam_cbdv_cl10 <- pam(rsn_dyn_cbdv_0509[, 14:33], k=10, diss = FALSE, metric = "manhattan", pamonce = 4, stand = FALSE) 
pam_cbdv_cl10$clusinfo
pam_cbdv_cl10$id.med # 12508  8229 11554  1894  1897 10632  7804  8153  7802  8151
# 12754  8397 11800  1894  8475  1897 10878  8399  8048  8050
pam_cbdv_cl10$medoids
# pam_cl10_clara <- clara(rsn_dyn_cbd[, 10:29], k = 10, metric = "manhattan", stand = FALSE, samples = 15, sampsize = 10000, pamLike = FALSE) 
rsn_dyn_cbdv_2808$clu10 <- pam_cbdv_cl10$clustering

pam_cbdv_cl8 <- pam(rsn_dyn_cbdv_0509[, 14:33], k=8, diss = FALSE, metric = "manhattan", pamonce = 4, stand = FALSE) 
pam_cbdv_cl8$clusinfo
pam_cbdv_cl8$id.med # 11318 12508  1874 11554  8453  8151  7804  6659
# 12754  8478 12295  1894  8399  8048  8397  8050
pam_cbdv_cl8$medoids
rsn_dyn_cbdv_2808$clu8 <- pam_cbdv_cl8$clustering

pam_cbdv_cl12 <- pam(rsn_dyn_cbdv_0509[, 14:33], k=12, diss = FALSE, metric = "manhattan", pamonce = 4, stand = FALSE) 
pam_cbdv_cl12$clusinfo
pam_cbdv_cl12$id.med 
# 12754  8478 12295  1894  8399  8048  8397  8050
pam_cbdv_cl12$medoids
rsn_dyn_cbdv_2808$clu8 <- pam_cbdv_cl8$clustering

pam_cbdv_cl6 <- pam(rsn_dyn_cbdv_0509[, 14:33], k=6, diss = FALSE, metric = "manhattan", pamonce = 4, stand = FALSE) 
pam_cbdv_cl6$clusinfo
pam_cbdv_cl6$id.med # 11318 12508  1874  8453  8151  6659
# 12754  1874  1894  8397  8399  8050
pam_cbdv_cl6$medoids
rsn_dyn_cbdv_2808$clu6 <- pam_cbdv_cl6$clustering

medoids_pam_cbdv_12 <- rbind(as.data.frame(pam_cbdv_cl6$medoids),as.data.frame(pam_cbdv_cl8$medoids), as.data.frame(pam_cbdv_cl10$medoids), as.data.frame(pam_cbdv_cl12$medoids))

pam_cbdv_cl10 <- pam(rsn_dyn_cbdv_0509[, 14:33], k=10, diss = FALSE, metric = "manhattan", pamonce = 4, stand = FALSE) 
?cluster::pam
pam_cbdv_cl12 <- pam(rsn_dyn_cbdv_0509[, 14:33], k=12, diss = FALSE, metric = "manhattan", pamonce = 4, stand = FALSE) 
rsn_dyn_cbdv_0509$clu12 <- pam_cbdv_cl12$clustering
rsn_dyn_cbdv_0509$clu8 <- pam_cbdv_cl8$clustering
rsn_dyn_cbdv_0509$clu6 <- pam_cbdv_cl6$clustering
write.xlsx(medoids_pam_cbdv_12, "medoids_pam_cbdv_12.xlsx")
write.xlsx(rsn_dyn_cbdv_0509, "rsn_dyn_cbdv_0509.xlsx")

medoids_pam_cbdv_new_31mar <- rbind(as.data.frame(pam_cbdv_cl6$medoids),as.data.frame(pam_cbdv_cl8$medoids), as.data.frame(pam_cbdv_cl10$medoids), as.data.frame(pam_cbdv_cl12$medoids))
write.xlsx(medoids_pam_cbdv_new_31mar, "medoids_pam_cbdv_new_31mar.xlsx")

rsn_dyn_cbdv_0509$clu12 <- pam_cbdv_cl12$clustering
rsn_dyn_cbdv_0509$clu10 <- pam_cbdv_cl10$clustering
rsn_dyn_cbdv_0509$clu8 <- pam_cbdv_cl8$clustering
rsn_dyn_cbdv_0509$clu6 <- pam_cbdv_cl6$clustering
write.xlsx(rsn_dyn_cbdv_0509, "rsn_dyn_cbdv_3103.xlsx")
```
# FO calculation
## original data
```{r}
fo_cbdv <- read.xlsx("/Users/yange/YANGE/Phd/DFC/CBD/fo_cbdv_0509.xlsx")
fo_cl10_cbdv <- fo_cbdv %>% 
  dplyr::select(id_sess, cl10_fo, cluster) %>% 
  pivot_wider(names_from = cluster, names_prefix = "clu", values_from = cl10_fo)
fo_cl10_cbdv <- core_network_strength_cbd %>% 
  full_join(fo_cl10_cbdv) %>% 
  filter(drug != "1")
```
### Baseline differences: 10 
```{r}
fo_cl10_cbdv_plb <- fo_cl10_cbdv %>% 
  filter(drug == "0")
summary(lm(data = fo_cl10_cbdv_plb, scale(clu10) ~ asd + scale(age)  + scale(IQ) + scale(meanFD_246))) 
# aasd1                1.1503     0.3708   3.102  0.00458 **
summary(lm(data = fo_cl10_cbdv_plb, scale(clu10) ~ asd + scale(age)  + scale(IQ) + scale(meanFD_246) + order))

```
### Interaction
```{r}
summary(lmerTest::lmer(data = fo_cl10_cbdv, scale(clu1) ~ drug + asd + scale(age)  + scale(IQ) + scale(meanFD_246) + (1|id)))
# drug2:asd1         -0.3616     0.5424 29.0611  -0.667    0.510
summary(lmerTest::lmer(data = fo_cl10_cbdv, scale(clu2) ~ drug + asd + scale(age)  + scale(IQ) + scale(meanFD_246) + (1|id)))
# drug2:asd1          0.1206     0.4466 23.5921   0.270 0.789436
summary(lmerTest::lmer(data = fo_cl10_cbdv, scale(clu3) ~ drug + asd + scale(age)  + scale(IQ) + scale(meanFD_246) + (1|id)))
# asd1               0.746942   0.358325 29.294392   2.085   0.0459 *
# drug2:asd1          0.6712     0.5432 29.4224   1.236    0.226
summary(lmerTest::lmer(data = fo_cl10_cbdv, scale(clu4) ~ drug + asd + scale(age)  + scale(IQ) + scale(meanFD_246) + (1|id)))
# drug2:asd1         0.73967    0.42989 25.72342   1.721   0.0973
summary(lmerTest::lmer(data = fo_cl10_cbdv, scale(clu5) ~ drug + asd + scale(age)  + scale(IQ) + scale(meanFD_246) + (1|id)))
# drug2:asd1        -0.67163    0.56900 45.00000  -1.180   0.2441
summary(lmerTest::lmer(data = fo_cl10_cbdv, scale(clu6) ~ drug + asd + scale(age)  + scale(IQ) + scale(meanFD_246) + (1|id)))
# drug2:asd1          0.3257     0.4871 24.9752   0.669    0.510
summary(lmerTest::lmer(data = fo_cl10_cbdv, scale(clu7) ~ drug + asd + scale(age)  + scale(IQ) + scale(meanFD_246) + (1|id)))
# drug2:asd1         0.80100    0.51910 27.77264   1.543   0.1341 
summary(lmerTest::lmer(data = fo_cl10_cbdv, scale(clu8) ~ drug + asd + scale(age)  + scale(IQ) + scale(meanFD_246) + (1|id)))
# drug2:asd1         0.075134   0.437519 28.671004   0.172 0.864858
summary(lmerTest::lmer(data = fo_cl10_cbdv, scale(clu9) ~ drug + asd + scale(age)  + scale(IQ) + scale(meanFD_246) + (1|id)))
# drug2:asd1         -0.3714     0.5449 29.1130  -0.682   0.5009
summary(lmerTest::lmer(data = fo_cl10_cbdv, scale(clu10) ~ drug + asd + scale(age)  + scale(IQ) + scale(meanFD_246) + (1|id)))
# drug2:asd1        -0.622434   0.560380 30.547589  -1.111   0.2753 

summary(lmerTest::lmer(data = dwt_cl10_cbdv, scale(clu10) ~ drug * asd + scale(age)  + scale(IQ) + scale(meanFD_246) + (1|order) + (1|id)))
summary(lmerTest::lmer(data = dwt_cl10_cbdv, scale(clu1) ~ drug * asd + scale(age)  + scale(IQ) + scale(meanFD_246) + (1|order) + (1|id)))
```
## 12 clusters
```{r}
n_cl12_block <- rsn_dyn_cbdv_3103 %>%
  group_by(id_sess) %>% 
  count(clu12) %>% 
  rename("cl12_n" = n) 
n_subject <- rsn_dyn_cbdv_3103 %>%
  group_by(id_sess) %>% 
  count() 
fo_cbdv_cl12 <- n_cl12_block %>% 
  full_join(n_subject) %>% 
  mutate( "perc" = cl12_n/n) %>% 
  select(-"cl12_n", -"n") 
fo_cl12_0104 <- fo_cbdv_cl12 %>% 
  pivot_wider(names_from = clu12, names_prefix = "fo_clu", values_from = perc)
write.xlsx(fo_cl12_0104, "fo_cl12_0104.xlsx")
```

## 10 clusters
```{r}
n_cl10_block <- rsn_dyn_cbdv_3103 %>%
  group_by(id_sess) %>% 
  count(clu10) %>% 
  rename("cl10_n" = n) 
n_subject <- rsn_dyn_cbdv_3103 %>%
  group_by(id_sess) %>% 
  count() 
fo_cbdv_cl10 <- n_cl10_block %>% 
  full_join(n_subject) %>% 
  mutate( "perc" = cl10_n/n) %>% 
  select(-"cl10_n", -"n") 
fo_cl10_0104 <- fo_cbdv_cl10 %>% 
  pivot_wider(names_from = clu10, names_prefix = "fo_clu", values_from = perc)
write.xlsx(fo_cl10_0104, "fo_cl10_0104.xlsx")
```

## 8 clusters
```{r}
n_cl8_block <- rsn_dyn_cbdv_3103 %>%
  group_by(id_sess) %>% 
  count(clu8) %>% 
  rename("cl8_n" = n) 
n_subject <- rsn_dyn_cbdv_3103 %>%
  group_by(id_sess) %>% 
  count() 
fo_cbdv_cl8 <- n_cl8_block %>% 
  full_join(n_subject) %>% 
  mutate( "perc" = cl8_n/n) %>% 
  select(-"cl8_n", -"n") 
fo_cl8_0104 <- fo_cbdv_cl8 %>% 
  pivot_wider(names_from = clu8, names_prefix = "fo_clu", values_from = perc)
write.xlsx(fo_cl8_0104, "fo_cl8_0104.xlsx")
```
## 6 clusters
```{r}
n_cl6_block <- rsn_dyn_cbdv_3103 %>%
  group_by(id_sess) %>% 
  count(clu6) %>% 
  rename("cl6_n" = n) 
n_subject <- rsn_dyn_cbdv_3103 %>%
  group_by(id_sess) %>% 
  count() 
fo_cbdv_cl6 <- n_cl6_block %>% 
  full_join(n_subject) %>% 
  mutate( "perc" = cl6_n/n) %>% 
  select(-"cl6_n", -"n") 
fo_cl6_0104 <- fo_cbdv_cl6 %>% 
  pivot_wider(names_from = clu6, names_prefix = "fo_clu", values_from = perc)
write.xlsx(fo_cl6_0104, "fo_cl6_0104.xlsx")
```
## DT original data
```{r}
dwt_cbdv <- read.xlsx("/Users/yange/YANGE/Phd/DFC/CBD/dwt_cbdv_0509.xlsx")
dwt_cl10_cbdv <- dwt_cbdv %>% 
  dplyr::select(id_sess, dwt_cl10, cluster) %>% 
  pivot_wider(names_from = cluster, names_prefix = "clu", values_from = dwt_cl10)
dwt_cl10_cbdv <- core_network_strength_cbd %>% 
  full_join(dwt_cl10_cbdv) %>% 
  filter(drug != "1")
dwt_cl10_cbdv$asd <- as.factor(dwt_cl10_cbdv$asd)
dwt_cl10_cbdv$drug <- as.factor(dwt_cl10_cbdv$drug)
dwt_cl10_cbdv <- dwt_cl10_cbdv %>% 
  separate(id_sess, into = c("id", "order"), sep = -1, remove = FALSE)
dwt_cl10_cbdv$order<- as.factor(dwt_cl10_cbdv$order)
dwt_cl10_cbdv$id <- as.character(dwt_cl10_cbdv$id)
```

### Baseline differences: 10 
```{r}
dwt_cl10_cbdv_plb <- dwt_cl10_cbdv %>% 
  filter(drug == "0")
summary(lm(data = dwt_cl10_cbdv_plb, scale(clu10) ~ asd + scale(age)  + scale(IQ) + scale(meanFD_246))) 
# asd1         1.34014    0.43107   3.109  0.00451 **
summary(lm(data = dwt_cl10_cbdv_plb, scale(clu10) ~ asd + scale(age)  + scale(IQ) + scale(meanFD_246) + order))

```
### Interaction
```{r}
summary(lmerTest::lmer(data = dwt_cl10_cbdv, scale(clu1) ~ drug + asd + scale(age)  + scale(IQ) + scale(meanFD_246) + (1|id)))
# drug2:asd1        -0.34286    0.54181 28.71714  -0.633    0.532
summary(lmerTest::lmer(data = dwt_cl10_cbdv, scale(clu2) ~ drug + asd + scale(age)  + scale(IQ) + scale(meanFD_246) + (1|id)))
# drug2:asd1         0.02847    0.47906 26.11525   0.059  0.95306 
summary(lmerTest::lmer(data = dwt_cl10_cbdv, scale(clu3) ~ drug + asd + scale(age)  + scale(IQ) + scale(meanFD_246) + (1|id)))
# drug2:asd1         0.02446    0.54642 30.52879   0.045    0.965
summary(lmerTest::lmer(data = dwt_cl10_cbdv, scale(clu4) ~ drug + asd + scale(age)  + scale(IQ) + scale(meanFD_246) + (1|id)))
# drug2:asd1        -0.124544   0.518543 27.487306  -0.240   0.8120 
summary(lmerTest::lmer(data = dwt_cl10_cbdv, scale(clu5) ~ drug + asd + scale(age)  + scale(IQ) + scale(meanFD_246) + (1|id)))
# drug2:asd1         0.10242    0.61675 45.00000   0.166    0.869
summary(lmerTest::lmer(data = dwt_cl10_cbdv, scale(clu6) ~ drug * asd + scale(age)  + scale(IQ) + scale(meanFD_246) + (1|id)))
# drug2              0.62449    0.32249 23.47075   1.936   0.0649 .
# asd1               0.95596    0.45020 39.53593   2.123   0.0400 *
# drug2:asd1        -1.36704    0.53005 28.66413  -2.579   0.0153 *
summary(lmerTest::lmer(data = dwt_cl10_cbdv, scale(clu7) ~ drug + asd + scale(age)  + scale(IQ) + scale(meanFD_246) + (1|id)))
# drug2              0.21567    0.35966 22.27465   0.600   0.5548  
# asd1               0.43240    0.44818 41.27234   0.965   0.3403
# drug2:asd1        -0.99502    0.58090 27.29501  -1.713   0.0981
summary(lmerTest::lmer(data = dwt_cl10_cbdv, scale(clu8) ~ drug + asd + scale(age)  + scale(IQ) + scale(meanFD_246) + (1|id)))
# drug2              0.32088    0.35383 45.00000   0.907   0.3693  
# asd1              -0.06669    0.42583 45.00000  -0.157   0.8762 
# drug2:asd1        -0.24222    0.56836 45.00000  -0.426   0.6720
summary(lmerTest::lmer(data = dwt_cl10_cbdv, scale(clu9) ~ drug + asd + scale(age)  + scale(IQ) + scale(meanFD_246) + (1|id)))
# drug2             -0.16812    0.34243 24.13552  -0.491    0.628
# asd1              -0.24167    0.44348 41.07920  -0.545    0.589
# drug2:asd1         0.77186    0.55639 29.11808   1.387    0.176
summary(lmerTest::lmer(data = dwt_cl10_cbdv, scale(clu10) ~ drug * asd + scale(age)  + scale(IQ) + scale(meanFD_246) + (1|id)))
# drug2              0.73151    0.34868 45.00000   2.098  0.04156 * 
# asd1               1.13460    0.41964 45.00000   2.704  0.00964 **
# drug2:asd1        -1.43009    0.56009 45.00000  -2.553  0.01413 * 

summary(lmerTest::lmer(data = dwt_cl10_cbdv, scale(clu10) ~ drug * asd + scale(age)  + scale(IQ) + scale(meanFD_246) + (1|order) + (1|id)))
summary(lmerTest::lmer(data = dwt_cl10_cbdv, scale(clu1) ~ drug * asd + scale(age)  + scale(IQ) + scale(meanFD_246) + (1|order) + (1|id)))
```
# DT calculation
```{r}
dwt_cbdv_cl12_block <-unnest(nest_dwell(rsn_dyn_cbdv_3103, vars=c('id_sess'), foVar='clu12', sortBy=c('timepoint')), cols = c(data))
dwt_cbdv_cl10_block <-unnest(nest_dwell(rsn_dyn_cbdv_3103, vars=c('id_sess'), foVar='clu10', sortBy=c('timepoint')), cols = c(data))
dwt_cbdv_cl8_block <-unnest(nest_dwell(rsn_dyn_cbdv_3103, vars=c('id_sess'), foVar='clu8', sortBy=c('timepoint')), cols = c(data))
dwt_cbdv_cl6_block <-unnest(nest_dwell(rsn_dyn_cbdv_3103, vars=c('id_sess'), foVar='clu6', sortBy=c('timepoint')), cols = c(data))
dt_cl6_cbdv <- dwt_cbdv_cl6_block %>% 
  pivot_wider(names_from = cluster, names_prefix = "dt_clu", values_from = mean_dwell)
dt_cl8_cbdv <- dwt_cbdv_cl8_block %>% 
  pivot_wider(names_from = cluster, names_prefix = "dt_clu", values_from = mean_dwell)
dt_cl10_cbdv <- dwt_cbdv_cl10_block %>% 
  pivot_wider(names_from = cluster, names_prefix = "dt_clu", values_from = mean_dwell)
dt_cl12_cbdv <- dwt_cbdv_cl12_block %>% 
  pivot_wider(names_from = cluster, names_prefix = "dt_clu", values_from = mean_dwell)
write.xlsx(dt_cl12_cbdv, "dt_cl12_cbdv_0104.xlsx")
write.xlsx(dt_cl10_cbdv, "dt_cl10_cbdv_0104.xlsx")
write.xlsx(dt_cl8_cbdv, "dt_cl8_cbdv_0104.xlsx")
write.xlsx(dt_cl6_cbdv, "dt_cl6_cbdv_0104.xlsx")

dwellCount <- function(x){

  f <- c(which(diff(x) != 0),length(x))

  y2 <- c(f[1],diff(f))
  y1 <- x[f]

  y <- list("cluster" = y1,
            "dwell" = y2)

  return(y)
}

vars_ <- dplyr::syms(vars)
  vars__ <- dplyr::syms(append(vars, 'cluster'))
  srt_ <- dplyr::syms(sortBy)

nest_dwell <- function(tbl, vars, foVar, sortBy){

  require(dplyr)
  require(tidyr)
  require(janitor)

  vars_ <- dplyr::syms(vars)
  vars__ <- dplyr::syms(append(vars, 'cluster'))
  srt_ <- dplyr::syms(sortBy)

  tbl %>%
    dplyr::rename('clus' = all_of(foVar)) %>%
    dplyr::group_by(!!!vars_) %>%
    dplyr::arrange(!!!srt_) %>%
    dplyr::summarise(clus = list(clus)) %>%
    dplyr::mutate(cluster = purrr::map(clus, dwellCount)) %>%
    tidyr::unnest_wider(cluster) %>%
    dplyr::select(-clus) %>%
    tidyr::unnest(c(cluster, dwell)) %>%
    dplyr::ungroup() %>%
    # dplyr::filter(dwell != 1) %>%
    dplyr::group_by(!!!vars__) %>%
    dplyr::summarise(mean_dwell = mean(dwell)) %>%
    dplyr::mutate(cluster = as.character(cluster)) %>%
    dplyr::group_by(cluster) %>%
    tidyr::nest()

}
```

## Baseline: 6
```{r}
dt_cl6_cbdv <- read.xlsx("/Users/yange/YANGE/Phd/DFC/CBD/dt_cl6_cbdv_0104.xlsx")
dt_cl6_cbdv[, 2:7][is.na(dt_cl6_cbdv[,2:7])] <- 0
dt_cl6_cbdv <- core_network_strength_cbd %>% 
  select(id_sess, meanFD_246, , subject_id, id, asd, drug, `cbd/v`, age, IQ) %>% 
  right_join(dt_cl6_cbdv)
dt_cl6_plb <- dt_cl6_cbdv %>% 
  filter(drug == "0")
summary(lm(data = dt_cl6_plb, scale(dt_clu1) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = dt_cl6_plb, scale(dt_clu2) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = dt_cl6_plb, scale(dt_clu3) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = dt_cl6_plb, scale(dt_clu4) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = dt_cl6_plb, scale(dt_clu5) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = dt_cl6_plb, scale(dt_clu6) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))

fo_cl6_0104[, 2:7][is.na(fo_cl6_0104[,2:7])] <- 0
fo_cl6_0104 <- core_network_strength_cbd %>% 
  select(id_sess, meanFD_246, , subject_id, id, asd, drug, `cbd/v`, age, IQ) %>% 
  right_join(fo_cl6_0104)
fo_cl6_plb <- fo_cl6_0104 %>% 
  filter(drug == "0")
summary(lm(data = fo_cl6_plb, scale(fo_clu1) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = fo_cl6_plb, scale(fo_clu2) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = fo_cl6_plb, scale(fo_clu3) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = fo_cl6_plb, scale(fo_clu4) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = fo_cl6_plb, scale(fo_clu5) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = fo_cl6_plb, scale(fo_clu6) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
# asd1               1.02525    0.41289   2.483   0.0198 *
fo_cl6_plb$RES_fo_cl6 <- resid(lm(data = fo_cl6_plb, scale(fo_clu6) ~ scale(age) + scale(IQ) + scale(meanFD_246)))
```
### visual
```{r}
library(ggrain)
ggplot(fo_cl6_plb, aes(asd, RES_fo_cl6, fill = asd)) +
  geom_rain(alpha = .5, point.args = list(size = 2)) +
  theme_classic() +
  # scale_fill_brewer(palette = 'PRGn') +
  coord_cartesian() + # coord
  labs(
    x = "Groups",
    y = "Fractional Occupancy of State 6 (Residuals)"
    # color = "Groups"
  ) +
  scale_fill_manual(values=c("dodgerblue", "darkorange"), labels=c('Non-autistic', 'Autistic')) +
  guides(color = 'none', fill = 'none') +
 # scale_fill_manual(values = fils) +
  scale_x_discrete(labels=c('Non-autistic', 'Autistic')) +
  theme(
    plot.margin = unit(c(0.5,0.5,0.5,0.5),"cm"),
    panel.background = element_blank(),
    axis.line = element_line(color = "black"),
    axis.title = element_text(size = 12, color = "black",
                              face = "bold"),
    axis.text= element_text(size = 10, color = "black"),
    axis.text.x = element_text(margin = margin(t = 10, b = 3)),
    axis.text.y = element_text(size = 10, margin = margin(r = 10, l = 3)),
    legend.position.inside = c(0.92,0.9),
    legend.background = element_rect(colour = "black"),
    legend.text = element_text(size = 10),
    legend.margin = margin(t=5, l=5,r=5,b=5)
  )
```


## Interaction: 6
```{r}
dt_cl6_cbdv <- core_network_strength_cbd %>% 
  select(id_sess, meanFD_246, , subject_id, id, asd, drug, `cbd/v`, age, IQ) %>% 
  right_join(dt_cl8_cbdv)
dt_cl6_cbdv_ny <- dt_cl6_cbdv %>% 
  filter(asd == "0")
dt_cl6_cbdv_asd <- dt_cl6_cbdv %>% 
  filter(asd == "1")
summary(lmerTest::lmer(data = dt_cl6_cbdv, scale(dt_clu1) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = dt_cl6_cbdv, scale(dt_clu2) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = dt_cl6_cbdv, scale(dt_clu3) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = dt_cl6_cbdv, scale(dt_clu4) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = dt_cl6_cbdv, scale(dt_clu5) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = dt_cl6_cbdv, scale(dt_clu6) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
# drug2              0.86335    0.34895 23.02471   2.474   0.0212 *
# drug2:asd1        -1.25635    0.56061 27.92977  -2.241   0.0332 *
summary(lmerTest::lmer(data = dt_cl6_cbdv_ny, scale(dt_clu6) ~ drug + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
# drug2              0.96269    0.22612 10.49181   4.257   0.0015 **
summary(lmerTest::lmer(data = dt_cl6_cbdv_asd, scale(dt_clu6) ~ drug + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
# drug2             -0.375708   0.513570 17.000000  -0.732    0.474
dt_cl6_cbdv$RES_dt_cl6 <- resid(lm(data = dt_cl6_cbdv, scale(dt_clu6) ~ scale(age) + scale(IQ) + scale(meanFD_246)))

fo_cl6_0104 <- core_network_strength_cbd %>% 
  select(id_sess, meanFD_246, , subject_id, id, asd, drug, `cbd/v`, age, IQ) %>% 
  right_join(fo_cl6_0104)
summary(lmerTest::lmer(data = fo_cl6_0104, scale(fo_clu1) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = fo_cl6_0104, scale(fo_clu2) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
# drug2             -0.49233    0.22623 23.21345  -2.176   0.0400 *
summary(lmerTest::lmer(data = fo_cl6_0104, scale(fo_clu3) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = fo_cl6_0104, scale(fo_clu4) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = fo_cl6_0104, scale(fo_clu5) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = fo_cl6_0104, scale(fo_clu6) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
```
### Visual
```{r}
mean_dt_cl6 <- dt_cl6_cbdv %>% 
  group_by(asd, drug) %>% 
  summarise(mean_RES_dt_clu6 = mean(RES_dt_cl6))
level_order <- c('0', '2') 
cols <-c('orange','steelblue2')
fils <- c('orange1','steelblue1')
dt_cl6_cbdv %>% 
  ggplot(aes(x = factor(drug, level = level_order), RES_dt_cl6, fill = asd, color = asd, shape = asd)) +
  geom_line(data = mean_dt_cl6,aes(x = factor(drug, level = level_order), y = mean_RES_dt_clu6, group = asd), linewidth =1.5) +
  geom_rain(rain.side = 'f2x2', id.long.var = "id",
            violin.args = list(color = NA, alpha = .5),
            boxplot.args = list(width = .07, alpha = .5),
            point.args = list(size = 2.2),
            boxplot.args.pos = list(
                position = ggpp::position_dodgenudge(width = .1, #width needed now in ggpp version 0.5.g
                  x = c(-.1, -.4, # pre versicolor, pre virginica
                        .1, .4)))
            # post; post
           ) + #post; post 
  theme_classic() +
  #scale_fill_brewer(palette = 'PRGn') +
  #scale_color_brewer(palette = 'PRGn', labels=c('Non-autistic', 'Autistic')) +
  # scale_fill_brewer(palette = 'PRGn', labels=c('Non-autistic', 'Autistic')) +
  # scale_color_brewer(palette = 'PRGn')  +
  scale_fill_manual(values=c("dodgerblue", "darkorange")) +
   # scale_color_manual(values=c("dodgerblue", "darkorange"), labels=c('Non-autistic', 'Autistic')) +
  scale_colour_manual(name = "Groups",
                      labels = c('Non-autistic', 'Autistic'),
                      values = c("dodgerblue", "darkorange")) +   
  scale_shape_manual(name = "Groups",
                     labels = c('Non-autistic', 'Autistic'),
                     values = c(1, 2)) +
  guides(fill = 'none') +
#  stat_boxplot(aes(color= asd), geom="errorbar",position=position_dodge(width=0.5),width=0.1) + 
#  geom_boxplot(aes(fill = asd),position=position_dodge(width =0.5),width=0.4) + 
#  geom_line(aes( group= id, color = asd)) + 
#  geom_point(aes(fill=asd,color = asd, group= id ),pch=21) + 
#  stat_pvalue_manual(df_p_val1,label = "p.adj.signif",label.size=6,hide.ns = T) + # p values
  coord_cartesian() + # coord
  labs(
    x = "Drugs",
    y = "Dwell Time of State 6 (Residuals)"
  ) +
  # scale_fill_manual(labels=c('Non-autistic', 'Autistic')) + # 
  # scale_fill_manual(values = fils) +
  scale_x_discrete(labels=c('Placebo', 'CBDV')) +
  theme(
    plot.margin = unit(c(0.5,0.5,0.5,0.5),"cm"),
    panel.background = element_blank(),
    axis.line = element_line(color = "black"),
    axis.title = element_text(size = 12, color = "black",
                              face = "bold"),
    axis.text= element_text(size = 10, color = "black"),
    axis.text.x = element_text(margin = margin(t = 10, b = 3)),
    axis.text.y = element_text(size = 10, margin = margin(r = 10, l = 3)),
    # legend.position = c(0.95,0.85),
    legend.background = element_rect(colour = "black"),
    legend.title = element_text(size = 9, color = "black",
                              face = "bold"),
    legend.text = element_text(size = 8),
    legend.margin = margin(t=2, l=2,r=2,b=2)
  )
```

## Baseline: 8
```{r}
dt_cl8_cbdv <- read.xlsx("/Users/yange/YANGE/Phd/DFC/CBD/dt_cl8_cbdv_0104.xlsx")
dt_cl8_cbdv[, 2:9][is.na(dt_cl8_cbdv[,2:9])] <- 0
dt_cl8_cbdv <- core_network_strength_cbd %>% 
  select(id_sess, meanFD_246, , subject_id, id, asd, drug, `cbd/v`, age, IQ) %>% 
  right_join(dt_cl8_cbdv)

dt_cl8_plb <- dt_cl8_cbdv %>% 
  filter(drug == "0")
summary(lm(data = dt_cl8_plb, scale(dt_clu1) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = dt_cl8_plb, scale(dt_clu2) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = dt_cl8_plb, scale(dt_clu3) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = dt_cl8_plb, scale(dt_clu4) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = dt_cl8_plb, scale(dt_clu5) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = dt_cl8_plb, scale(dt_clu6) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = dt_cl8_plb, scale(dt_clu7) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = dt_cl8_plb, scale(dt_clu8) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))

fo_cl8_0104[, 2:9][is.na(fo_cl8_0104[,2:9])] <- 0
fo_cl8_0104 <- core_network_strength_cbd %>% 
  select(id_sess, meanFD_246, , subject_id, id, asd, drug, `cbd/v`, age, IQ) %>% 
  right_join(fo_cl8_0104)
fo_cl8_plb <- fo_cl8_0104 %>% 
  filter(drug == "0")
summary(lm(data = fo_cl8_plb, scale(fo_clu1) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = fo_cl8_plb, scale(fo_clu2) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = fo_cl8_plb, scale(fo_clu3) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = fo_cl8_plb, scale(fo_clu4) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = fo_cl8_plb, scale(fo_clu5) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = fo_cl8_plb, scale(fo_clu6) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = fo_cl8_plb, scale(fo_clu7) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = fo_cl8_plb, scale(fo_clu8) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
# asd1               0.85189    0.38956   2.187  0.03795 *
fo_cl8_plb$RES_fo_cl8 <- resid(lm(data = fo_cl8_plb, scale(fo_clu8) ~ scale(age) + scale(IQ) + scale(meanFD_246)))

```

```{r}
ggplot(fo_cl8_plb, aes(asd, RES_fo_cl8, fill = asd)) +
  geom_rain(alpha = .5, point.args = list(size = 2)) +
  theme_classic() +
  # scale_fill_brewer(palette = 'PRGn') +
  coord_cartesian() + # coord
  labs(
    x = "Groups",
    y = "Fractional Occupancy of State 8 (Residuals)"
    # color = "Groups"
  ) +
  scale_fill_manual(values=c("dodgerblue", "darkorange"), labels=c('Non-autistic', 'Autistic')) +
  guides(color = 'none', fill = 'none') +
 # scale_fill_manual(values = fils) +
  scale_x_discrete(labels=c('Non-autistic', 'Autistic')) +
  theme(
    plot.margin = unit(c(0.5,0.5,0.5,0.5),"cm"),
    panel.background = element_blank(),
    axis.line = element_line(color = "black"),
    axis.title = element_text(size = 12, color = "black",
                              face = "bold"),
    axis.text= element_text(size = 10, color = "black"),
    axis.text.x = element_text(margin = margin(t = 10, b = 3)),
    axis.text.y = element_text(size = 10, margin = margin(r = 10, l = 3)),
    legend.position.inside = c(0.92,0.9),
    legend.background = element_rect(colour = "black"),
    legend.text = element_text(size = 10),
    legend.margin = margin(t=5, l=5,r=5,b=5)
  )
```

## Interaction: 8
```{r}
dt_cl8_cbdv <- core_network_strength_cbd %>% 
  select(id_sess, meanFD_246, , subject_id, id, asd, drug, `cbd/v`, age, IQ) %>% 
  right_join(dt_cl8_cbdv)

summary(lmerTest::lmer(data = dt_cl8_cbdv, scale(dt_clu1) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = dt_cl8_cbdv, scale(dt_clu2) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = dt_cl8_cbdv, scale(dt_clu3) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
# asd1              -0.87994    0.34399 46.00000  -2.558   0.0139 *
summary(lmerTest::lmer(data = dt_cl8_cbdv, scale(dt_clu4) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = dt_cl8_cbdv, scale(dt_clu5) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = dt_cl8_cbdv, scale(dt_clu6) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = dt_cl8_cbdv, scale(dt_clu7) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = dt_cl8_cbdv, scale(dt_clu8) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))

fo_cl8_0104 <- core_network_strength_cbd %>% 
  select(id_sess, meanFD_246, , subject_id, id, asd, drug, `cbd/v`, age, IQ) %>% 
  right_join(fo_cl8_0104)
summary(lmerTest::lmer(data = fo_cl8_0104, scale(fo_clu1) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = fo_cl8_0104, scale(fo_clu2) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = fo_cl8_0104, scale(fo_clu3) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
# asd1              -0.957071   0.435534 40.106523  -2.197   0.0338 *
summary(lmerTest::lmer(data = fo_cl8_0104, scale(fo_clu4) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = fo_cl8_0104, scale(fo_clu5) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = fo_cl8_0104, scale(fo_clu6) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = fo_cl8_0104, scale(fo_clu7) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = fo_cl8_0104, scale(fo_clu8) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
```
## Baseline: 10
```{r}
dt_cl10_cbdv[, 2:11][is.na(dt_cl10_cbdv[,2:11])] <- 0
dt_cl10_cbdv <- core_network_strength_cbd %>% 
  select(id_sess, meanFD_246, , subject_id, id, asd, drug, `cbd/v`, age, IQ) %>% 
  right_join(dt_cl10_cbdv)
dt_cl10_plb <- dt_cl10_cbdv %>% 
  filter(drug == "0")
summary(lm(data = dt_cl10_plb, scale(dt_clu1) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = dt_cl10_plb, scale(dt_clu2) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = dt_cl10_plb, scale(dt_clu3) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = dt_cl10_plb, scale(dt_clu4) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = dt_cl10_plb, scale(dt_clu5) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = dt_cl10_plb, scale(dt_clu6) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = dt_cl10_plb, scale(dt_clu7) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = dt_cl10_plb, scale(dt_clu8) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = dt_cl10_plb, scale(dt_clu9) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = dt_cl10_plb, scale(dt_clu10) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
# asd1               1.27707    0.41078   3.109  0.00451 **

fo_cl10_0104[, 2:11][is.na(fo_cl10_0104[,2:11])] <- 0
fo_cl10_0104 <- core_network_strength_cbd %>% 
  select(id_sess, meanFD_246, , subject_id, id, asd, drug, `cbd/v`, age, IQ) %>% 
  right_join(fo_cl10_0104)
fo_cl10_plb <- fo_cl10_0104 %>% 
  filter(drug == "0")
summary(lm(data = fo_cl10_plb, scale(fo_clu1) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = fo_cl10_plb, scale(fo_clu2) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = fo_cl10_plb, scale(fo_clu3) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = fo_cl10_plb, scale(fo_clu4) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = fo_cl10_plb, scale(fo_clu5) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = fo_cl10_plb, scale(fo_clu6) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = fo_cl10_plb, scale(fo_clu7) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = fo_cl10_plb, scale(fo_clu8) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = fo_cl10_plb, scale(fo_clu9) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = fo_cl10_plb, scale(fo_clu10) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
# asd1                1.1503     0.3708   3.102  0.00458 **
```
## Interaction: 10
```{r}
dt_cl10_cbdv[, 2:11][is.na(dt_cl10_cbdv[,2:11])] <- 0
dt_cl10_cbdv <- core_network_strength_cbd %>% 
  select(id_sess, meanFD_246, , subject_id, id, asd, drug, `cbd/v`, age, IQ) %>% 
  right_join(dt_cl10_cbdv)

summary(lmerTest::lmer(data = dt_cl10_cbdv, scale(dt_clu1) ~ drug+asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = dt_cl10_cbdv, scale(dt_clu2) ~ drug+asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = dt_cl10_cbdv, scale(dt_clu3) ~ drug+asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = dt_cl10_cbdv, scale(dt_clu4) ~ drug+asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = dt_cl10_cbdv, scale(dt_clu5) ~ drug+asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = dt_cl10_cbdv, scale(dt_clu6) ~ drug*asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
# asd1               0.95596    0.45020 39.53593   2.123   0.0400 *
# drug2:asd1        -1.36704    0.53005 28.66413  -2.579   0.0153 *
summary(lmerTest::lmer(data = dt_cl10_cbdv, scale(dt_clu7) ~ drug+asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = dt_cl10_cbdv, scale(dt_clu8) ~ drug+asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = dt_cl10_cbdv, scale(dt_clu9) ~ drug+asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = dt_cl10_cbdv, scale(dt_clu10) ~ drug*asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
# drug2              0.73151    0.34868 45.00000   2.098  0.04156 * 
# asd1               1.13460    0.41964 45.00000   2.704  0.00964 **
# scale(age)         0.04711    0.14087 45.00000   0.334  0.73959   
# scale(IQ)         -0.13403    0.15204 45.00000  -0.882  0.38270   
# scale(meanFD_246) -0.47291    0.18765 45.00000  -2.520  0.01535 * 
# drug2:asd1        -1.43009    0.56009 45.00000  -2.553  0.01413 * 

fo_cl10_0104 <- core_network_strength_cbd %>% 
  select(id_sess, meanFD_246, , subject_id, id, asd, drug, `cbd/v`, age, IQ) %>% 
  right_join(fo_cl10_0104)
summary(lmerTest::lmer(data = fo_cl10_0104, scale(fo_clu1) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = fo_cl10_0104, scale(fo_clu2) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = fo_cl10_0104, scale(fo_clu3) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = fo_cl10_0104, scale(fo_clu4) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = fo_cl10_0104, scale(fo_clu5) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = fo_cl10_0104, scale(fo_clu6) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = fo_cl10_0104, scale(fo_clu7) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = fo_cl10_0104, scale(fo_clu8) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = fo_cl10_0104, scale(fo_clu9) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = fo_cl10_0104, scale(fo_clu10) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
```

## Baseline: 12
```{r}
dt_cl12_cbdv <- read.xlsx("/Users/yange/YANGE/Phd/DFC/CBD/dt_cl12_cbdv_0104.xlsx")
dt_cl12_cbdv[, 2:13][is.na(dt_cl12_cbdv[,2:13])] <- 0
dt_cl12_cbdv <- core_network_strength_cbd %>% 
  select(id_sess, meanFD_246, , subject_id, id, asd, drug, `cbd/v`, age, IQ) %>% 
  right_join(dt_cl12_cbdv)
dt_cl12_plb <- dt_cl12_cbdv %>% 
  filter(drug == "0")
summary(lm(data = dt_cl12_plb, scale(dt_clu1) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = dt_cl12_plb, scale(dt_clu2) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = dt_cl12_plb, scale(dt_clu3) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = dt_cl12_plb, scale(dt_clu4) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = dt_cl12_plb, scale(dt_clu5) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
# asd1                1.0533     0.4275   2.464   0.0207 *
dt_cl12_plb$RES_dt_cl5 <- resid(lm(data = dt_cl12_plb, scale(dt_clu5) ~ scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = dt_cl12_plb, scale(dt_clu6) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = dt_cl12_plb, scale(dt_clu7) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = dt_cl12_plb, scale(dt_clu8) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = dt_cl12_plb, scale(dt_clu9) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = dt_cl12_plb, scale(dt_clu10) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = dt_cl12_plb, scale(dt_clu11) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = dt_cl12_plb, scale(dt_clu12) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))

fo_cl12_0104[, 2:13][is.na(fo_cl12_0104[,2:13])] <- 0
fo_cl12_0104 <- core_network_strength_cbd %>% 
  select(id_sess, meanFD_246, , subject_id, id, asd, drug, `cbd/v`, age, IQ) %>% 
  right_join(fo_cl12_0104)
fo_cl12_plb <- fo_cl12_0104 %>% 
  filter(drug == "0")
summary(lm(data = fo_cl12_plb, scale(fo_clu1) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = fo_cl12_plb, scale(fo_clu2) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = fo_cl12_plb, scale(fo_clu3) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = fo_cl12_plb, scale(fo_clu4) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = fo_cl12_plb, scale(fo_clu5) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = fo_cl12_plb, scale(fo_clu6) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = fo_cl12_plb, scale(fo_clu7) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = fo_cl12_plb, scale(fo_clu8) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = fo_cl12_plb, scale(fo_clu9) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = fo_cl12_plb, scale(fo_clu10) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
# asd1               0.93823    0.40352   2.325  0.02814 * 
fo_cl12_plb$RES_fo_cl10 <- resid(lm(data = fo_cl12_plb, scale(fo_clu10) ~ scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = fo_cl12_plb, scale(fo_clu11) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
summary(lm(data = fo_cl12_plb, scale(fo_clu12) ~ asd + scale(age) + scale(IQ) + scale(meanFD_246)))
```

```{r}
ggplot(dt_cl12_plb, aes(asd, RES_dt_cl5, fill = asd)) +
  geom_rain(alpha = .5, point.args = list(size = 2)) +
  theme_classic() +
  # scale_fill_brewer(palette = 'PRGn') +
  coord_cartesian() + # coord
  labs(
    x = "Groups",
    y = "Dwell Time of State 5 (Residuals)"
    # color = "Groups"
  ) +
  scale_fill_manual(values=c("dodgerblue", "darkorange"), labels=c('Non-autistic', 'Autistic')) +
  guides(color = 'none', fill = 'none') +
 # scale_fill_manual(values = fils) +
  scale_x_discrete(labels=c('Non-autistic', 'Autistic')) +
  theme(
    plot.margin = unit(c(0.5,0.5,0.5,0.5),"cm"),
    panel.background = element_blank(),
    axis.line = element_line(color = "black"),
    axis.title = element_text(size = 12, color = "black",
                              face = "bold"),
    axis.text= element_text(size = 10, color = "black"),
    axis.text.x = element_text(margin = margin(t = 10, b = 3)),
    axis.text.y = element_text(size = 10, margin = margin(r = 10, l = 3)),
    legend.position.inside = c(0.92,0.9),
    legend.background = element_rect(colour = "black"),
    legend.text = element_text(size = 10),
    legend.margin = margin(t=5, l=5,r=5,b=5)
  )
```
```{r}
ggplot(fo_cl12_plb, aes(asd, RES_fo_cl10, fill = asd)) +
  geom_rain(alpha = .5, point.args = list(size = 2)) +
  theme_classic() +
  # scale_fill_brewer(palette = 'PRGn') +
  coord_cartesian() + # coord
  labs(
    x = "Groups",
    y = "Fractional Occupancy of State 10 (Residuals)"
    # color = "Groups"
  ) +
  scale_fill_manual(values=c("dodgerblue", "darkorange"), labels=c('Non-autistic', 'Autistic')) +
  guides(color = 'none', fill = 'none') +
 # scale_fill_manual(values = fils) +
  scale_x_discrete(labels=c('Non-autistic', 'Autistic')) +
  theme(
    plot.margin = unit(c(0.5,0.5,0.5,0.5),"cm"),
    panel.background = element_blank(),
    axis.line = element_line(color = "black"),
    axis.title = element_text(size = 12, color = "black",
                              face = "bold"),
    axis.text= element_text(size = 10, color = "black"),
    axis.text.x = element_text(margin = margin(t = 10, b = 3)),
    axis.text.y = element_text(size = 10, margin = margin(r = 10, l = 3)),
    legend.position.inside = c(0.92,0.9),
    legend.background = element_rect(colour = "black"),
    legend.text = element_text(size = 10),
    legend.margin = margin(t=5, l=5,r=5,b=5)
  )
```

## Interaction: 12
```{r}
dt_cl12_cbdv <- core_network_strength_cbd %>% 
  select(id_sess, meanFD_246, , subject_id, id, asd, drug, `cbd/v`, age, IQ) %>% 
  right_join(dt_cl12_cbdv)

summary(lmerTest::lmer(data = dt_cl12_cbdv, scale(dt_clu1) ~ drug+asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = dt_cl12_cbdv, scale(dt_clu2) ~ drug+asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = dt_cl12_cbdv, scale(dt_clu3) ~ drug+asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = dt_cl12_cbdv, scale(dt_clu4) ~ drug+asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = dt_cl12_cbdv, scale(dt_clu5) ~ drug*asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
# asd1               1.03653    0.44402 40.00098   2.334   0.0247 *
# drug2:asd1        -1.42782    0.52581 29.44270  -2.715   0.0110 *
dt_cl12_cbdv$RES_dt_cl5 <- resid(lm(data = dt_cl12_cbdv, scale(dt_clu5) ~ scale(age) + scale(IQ) + scale(meanFD_246)))
dt_cl12_cbdv_ny <- dt_cl12_cbdv %>% 
  filter(asd == "0")
dt_cl12_cbdv_asd <- dt_cl12_cbdv %>% 
  filter(asd == "1")
summary(lmerTest::lmer(data = dt_cl12_cbdv_ny, scale(dt_clu5) ~ drug + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
# drug2              0.71228    0.30224 12.83659   2.357    0.035 *
summary(lmerTest::lmer(data = dt_cl12_cbdv_asd, scale(dt_clu5) ~ drug + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
# drug2              -0.8337     0.4532 13.1212  -1.840   0.0885
summary(lmerTest::lmer(data = dt_cl12_cbdv, scale(dt_clu6) ~ drug+asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = dt_cl12_cbdv, scale(dt_clu7) ~ drug+asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = dt_cl12_cbdv, scale(dt_clu8) ~ drug+asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = dt_cl12_cbdv, scale(dt_clu9) ~ drug+asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = dt_cl12_cbdv, scale(dt_clu10) ~ drug*asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = dt_cl12_cbdv, scale(dt_clu11) ~ drug+asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = dt_cl12_cbdv, scale(dt_clu12) ~ drug+asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))

fo_cl12_0104 <- core_network_strength_cbd %>% 
  select(id_sess, meanFD_246, , subject_id, id, asd, drug, `cbd/v`, age, IQ) %>% 
  right_join(fo_cl12_0104)
summary(lmerTest::lmer(data = fo_cl12_0104, scale(fo_clu1) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = fo_cl12_0104, scale(fo_clu2) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = fo_cl12_0104, scale(fo_clu3) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
# asd1              -0.957071   0.435534 40.106523  -2.197   0.0338 *
summary(lmerTest::lmer(data = fo_cl12_0104, scale(fo_clu4) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = fo_cl12_0104, scale(fo_clu5) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = fo_cl12_0104, scale(fo_clu6) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = fo_cl12_0104, scale(fo_clu7) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = fo_cl12_0104, scale(fo_clu8) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = fo_cl12_0104, scale(fo_clu9) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = fo_cl12_0104, scale(fo_clu10) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = fo_cl12_0104, scale(fo_clu11) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
summary(lmerTest::lmer(data = fo_cl12_0104, scale(fo_clu12) ~ drug * asd + scale(age) + scale(IQ) + scale(meanFD_246) +(1|id)))
```
### Visual
```{r}
mean_dt_cl12 <- dt_cl12_cbdv %>% 
  group_by(asd, drug) %>% 
  summarise(mean_RES_dt_clu5 = mean(RES_dt_cl5))
level_order <- c('0', '2') 
cols <-c('orange','steelblue2')
fils <- c('orange1','steelblue1')
dt_cl12_cbdv %>% 
  ggplot(aes(x = factor(drug, level = level_order), RES_dt_cl5, fill = asd, color = asd, shape = asd)) +
  geom_line(data = mean_dt_cl12,aes(x = factor(drug, level = level_order), y = mean_RES_dt_clu5, group = asd), linewidth =1.5) +
  geom_rain(rain.side = 'f2x2', id.long.var = "id",
            violin.args = list(color = NA, alpha = .5),
            boxplot.args = list(width = .07, alpha = .5),
            point.args = list(size = 2.2),
            boxplot.args.pos = list(
                position = ggpp::position_dodgenudge(width = .1, #width needed now in ggpp version 0.5.g
                  x = c(-.1, -.4, # pre versicolor, pre virginica
                        .1, .4)))
            # post; post
           ) + #post; post 
  theme_classic() +
  #scale_fill_brewer(palette = 'PRGn') +
  #scale_color_brewer(palette = 'PRGn', labels=c('Non-autistic', 'Autistic')) +
  # scale_fill_brewer(palette = 'PRGn', labels=c('Non-autistic', 'Autistic')) +
  # scale_color_brewer(palette = 'PRGn')  +
  scale_fill_manual(values=c("dodgerblue", "darkorange")) +
   # scale_color_manual(values=c("dodgerblue", "darkorange"), labels=c('Non-autistic', 'Autistic')) +
  scale_colour_manual(name = "Groups",
                      labels = c('Non-autistic', 'Autistic'),
                      values = c("dodgerblue", "darkorange")) +   
  scale_shape_manual(name = "Groups",
                     labels = c('Non-autistic', 'Autistic'),
                     values = c(1, 2)) +
  guides(fill = 'none') +
#  stat_boxplot(aes(color= asd), geom="errorbar",position=position_dodge(width=0.5),width=0.1) + 
#  geom_boxplot(aes(fill = asd),position=position_dodge(width =0.5),width=0.4) + 
#  geom_line(aes( group= id, color = asd)) + 
#  geom_point(aes(fill=asd,color = asd, group= id ),pch=21) + 
#  stat_pvalue_manual(df_p_val1,label = "p.adj.signif",label.size=6,hide.ns = T) + # p values
  coord_cartesian() + # coord
  labs(
    x = "Drugs",
    y = "Dwell Time of State 5 (Residuals)"
  ) +
  # scale_fill_manual(labels=c('Non-autistic', 'Autistic')) + # 
  # scale_fill_manual(values = fils) +
  scale_x_discrete(labels=c('Placebo', 'CBDV')) +
  theme(
    plot.margin = unit(c(0.5,0.5,0.5,0.5),"cm"),
    panel.background = element_blank(),
    axis.line = element_line(color = "black"),
    axis.title = element_text(size = 12, color = "black",
                              face = "bold"),
    axis.text= element_text(size = 10, color = "black"),
    axis.text.x = element_text(margin = margin(t = 10, b = 3)),
    axis.text.y = element_text(size = 10, margin = margin(r = 10, l = 3)),
    # legend.position = c(0.95,0.85),
    legend.background = element_rect(colour = "black"),
    legend.title = element_text(size = 9, color = "black",
                              face = "bold"),
    legend.text = element_text(size = 8),
    legend.margin = margin(t=2, l=2,r=2,b=2)
  )
```
# clustering validation

### split-half datasets
```{r}
original_fit <- pam(rsn_dyn_cbdv_0509[, 14:33], k = 10, metric = "manhattan", pamonce = 4, stand = FALSE)
```

```{r}
# 1. Split data
set.seed(123)
# idx <- sample(seq_len(nrow(rsn_dyn_cbdv_3103[, 14:33])), size = floor(0.5 * nrow(rsn_dyn_cbdv_3103[, 14:33])))
# half2 <- rsn_dyn_cbdv_3103[, 14:33][-idx, ]
quater1 <- rsn_dyn_cbdv_3103 %>% 
  filter(timepoint <= 61 | (123 < timepoint & timepoint <= 185))
quater2 <- rsn_dyn_cbdv_3103 %>% 
  filter((61 < timepoint & timepoint <= 123)|timepoint > 185)
quater1_2 <- rsn_dyn_cbdv_3103 %>% 
   filter(timepoint <= 61 | timepoint > 184)
quater2_2 <- rsn_dyn_cbdv_3103 %>% 
   filter(61 < timepoint & timepoint <= 184)
# 2. Run PAM on both
pam_quater1 <- pam(quater1[, 14:33], k = 10, metric = "manhattan", pamonce = 4, stand = FALSE)
pam_quater2 <- pam(quater2[, 14:33], k = 10, metric = "manhattan", pamonce = 4, stand = FALSE)
pam_quater1_2 <- pam(quater1_2[, 14:33], k = 10, metric = "manhattan", pamonce = 4, stand = FALSE)
pam_quater2_2 <- pam(quater2_2[, 14:33], k = 10, metric = "manhattan", pamonce = 4, stand = FALSE)

# 3. Compare medoids (Spatial Correlation)
# This assumes features are spatial voxels/regions
cor_matrix_quater1 <- cor(t(original_fit$medoids), t(pam_quater1$medoids))
print(cor_matrix_quater1)
cor_matrix_quater2 <- cor(t(original_fit$medoids), t(pam_quater2$medoids))
print(cor_matrix_quater2)
cor_matrix_quater1 <- cor(t(original_fit$medoids), t(pam_quater1_2$medoids))
print(cor_matrix_quater1)
cor_matrix_quater2 <- cor(t(original_fit$medoids), t(pam_quater2_2$medoids))
print(cor_matrix_quater2)

split_quater_medoids <- rbind(as.data.frame(original_fit$medoids), as.data.frame(pam_quater1$medoids), as.data.frame(pam_quater2$medoids))
medoids <- c("org_clu1", "org_clu2", "org_clu3", "org_clu4", "org_clu5", "org_clu6", "org_clu7", "org_clu8", "org_clu9", "org_clu10", "half1_clu1", "half1_clu2", "half1_clu3", "half1_clu4", "half1_clu5", "half1_clu6", "half1_clu7", "half1_clu8", "half1_clu9", "half1_clu10", "half2_clu1", "half2_clu2", "half2_clu3", "half2_clu4", "half2_clu5", "half2_clu6", "half2_clu7", "half2_clu8", "half2_clu9", "half2_clu10")
split_quater_medoids$medoids <- medoids
write.xlsx(split_quater_medoids, "split_quater_medoids.xlsx")

split_quater_medoids <- read.xlsx("split_quater_medoids.xlsx")
original_fit <- split_quater_medoids[1:10, 1:20]
pam_quater2 <- split_quater_medoids[11:20, 1:20]
pam_quater1 <- split_quater_medoids[21:30, 1:20]
library(corrplot)
library(Hmisc)
library(RColorBrewer)
M_2 <- cor(t(original_fit), t(pam_quater2))
M_1 <- cor(t(original_fit), t(pam_quater1))
M_3 <- cor(t(pam_quater1), t(pam_quater2))
cor(t(original_fit), t(pam_quater1))
M_1[is.na(M_1)] <- 0
M_pos <- M_1
M_pos[M_pos < 0] <- 0
M_2[is.na(M_2)] <- 0
M_pos_2 <- M_2
M_pos_2[M_pos_2 < 0] <- 0
M_3[is.na(M_3)] <- 0
M_pos_3 <- M_3
M_pos_3[M_pos_3 < 0] <- 0

colnames(M_pos_2) <- c("1", "3", "4", "7", "6", "8", "10", "2", "9", "5")
colnames(M_pos) <- c("9", "1", "10", "4", "8", "6", "3", "5", "7", "2")

colnames(M_pos_3) <- c("1", "3", "4", "7", "6", "8", "10", "2", "9", "5")
rownames(M_pos_3) <- c("9", "1", "10", "4", "8", "6", "3", "5", "7", "2")

corrplot(M_pos, method="circle", order="alphabet", 
         # type="upper", 
         # addCoef.col = "black", # Add coefficient of correlation
         # tl.col="black", tl.srt=45, #Text label color and rotation
         col = brewer.pal(n=8, name="RdBu"),
         col.lim = c(0, 1) # Ensure the color scale stays anchored at -1 to 1
         # Combine with significance
         # p.mat = p.mat, sig.level = 0.01, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         # diag=FALSE 
         )

```


